Visual Diagnostics of a Model Explainer -- Tools for the Assessment of LIME Explanations

### 2020-09-16 paper.Rnw
fixed Figure 13 issue

# Create the explanation scatterplots
eoiM_3qb <-
  plot_explain_scatter(
    bullet_explain_perms_clean[1:3, ],
    alpha = 0.9,
    weights = TRUE,
    line_size = f13_ls
  ) +
  bullet_eoi_plot_theme +
  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
eoiNM_3qb <-
  plot_explain_scatter(
    bullet_explain_perms_clean[4:6, ],
    alpha = 0.9,
    weights = TRUE,
    line_size = f13_ls
  ) +
  bullet_eoi_plot_theme
eoiM_3eb <-
  plot_explain_scatter(
    bullet_explain_perms_clean[7:9, ],
    alpha = 0.9,
    weights = TRUE,
    line_size = f13_ls
  ) +
  bullet_eoi_plot_theme
eoiNM_3eb <-
  plot_explain_scatter(
    bullet_explain_perms_clean[10:12,],
    alpha = 0.9,
    weights = TRUE,
    line_size = f13_ls
  ) +
  bullet_eoi_plot_theme

>>>>

# Create the explanation scatterplots
eoiM_3qb <-
  plot_explain_scatter(
    bullet_explain_perms_clean[1:3, ],
    alpha = 0.9,
    weights = TRUE,
    line_size = f13_ls
  ) +
  bullet_eoi_plot_theme +
  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
eoiNM_3qb <-
  plot_explain_scatter(
    bullet_explain_perms_clean[4:6, ],
    alpha = 0.9,
    weights = TRUE,
    line_size = f13_ls
  ) +
  bullet_eoi_plot_theme +
  guides(linetype = guide_legend(override.aes = list(color = c("darkorange"))))
eoiM_3eb <-
  plot_explain_scatter(
    bullet_explain_perms_clean[7:9, ],
    alpha = 0.9,
    weights = TRUE,
    line_size = f13_ls
  ) +
  bullet_eoi_plot_theme
eoiNM_3eb <-
  plot_explain_scatter(
    bullet_explain_perms_clean[10:12,],
    alpha = 0.9,
    weights = TRUE,
    line_size = f13_ls
  ) +
  bullet_eoi_plot_theme
